% !TEX program = xelatex


%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.5in,top=0.6in,right=0.5in,bottom=0.6in]{geometry} % Document margins

\name{Andrew Kozlik}
\address{407-463-2268}
\address{akozlik@gmail.com}
\address{github.com/akozlik}

\begin{document}

%----------------------------------------------------------------------------------------
%	Profile
%----------------------------------------------------------------------------------------
\begin{rSection}{Profile}

    Product-focused technology leader with a proven track record of driving strategy, instilling technical excellence, and developing high-impact opportunities. Diverse career history spanning software development, engineering leadership, and product management at both cutting-edge startups and global technology providers.

\end{rSection}

%----------------------------------------------------------------------------------------
%	Experience
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

%------------------------------------------------

    \begin{rSubsection}{Contract Solutions Architect, at Brightline}{\bf September 2023 - Present}{}{}

    \item Oversaw technical delivery of a six month \$1.2M project implementing loyalty program launching in April
    \item Responsible for architecting high level solutions and breaking those solutions into actionable tasks the engineering team can complete.        
    \item Notification distribution center leveraging AWS Step Functions, Lambda, and. Expanded our notification deliverability beyond email into SMS + mobile push notifications.
    \item Design architecture to integrate Clutch gift card payemnts with Sqills S3 bookign engine to enable 
    \item Architected cancellation and modification fees to increase revenue by an estimated \$200K per month
    \item Architected real-time delay notifications to emplower end users with real-time status updates of their train departures
    \item Architected solutions for a variety of problems levrerasging AWS CloudFront, Lambda, API Gateway, DynamoDB, and Step Functions
    \item Provided work estimations and proposed schedules to the product team to give guidance on when key features could be delivered on their roadmap.    
    \item Identified inefficiencies in Brightline's delivery processes and solutioned changes leading to smoother delivery and more predictable outcomes.
    \item Architected a centralized notificaitons distribution center integrating real-time multi-channel notifications with various backend services
    \item Established an internal loop between customer support and product to get a pulse on customer needs and prioritize intiatives
    \item Coordinating between product, engineering, and PMO teams to ensure high-quality deliveries
    \item Built reporting and analyzed customer engagement data through A/B testing to further understand usage patterns and drive data-driven decisions

    \end{rSubsection}

    %------------------------------------------------


    \begin{rSubsection}{Head of Product, Mobile at eMeals.com}{\bf February 2022 - June 2023}{}{}

    \item Managed a team of 8 on-shore and near-shore team members spanning iOS, Android, web, support, and QA
    \item Led the redesign and development of RecipeBox to improve usability and user retention
    \item Oversaw migration RecipeBox's technolgoy stack to AWS-based technology to align with eMeals existing team expertise
    \item Integrate RecipeBox's core technology into the eMeals flagship app to give existing eMeals customers the ability to save recipes
    \item Oversaw development of a recipe seach feature to improve customer engagement and retention
    \item Improved eMeals' meal planning experience driving deeper engagement and conversion of trial customers
    \item Led the team to migrate eMeals' core Walmart shopping experience to a simplified one-tap experience
    \item Established an internal loop between customer support and product to get a pulse on customer needs and prioritize intiatives
    \item Built reporting and analyzed customer engagement data through A/B testing to further understand usage patterns and drive data-driven decisions

    \end{rSubsection}

    %------------------------------------------------

    \begin{rSubsection}{CEO at RecipeBox (acquired by eMeals.com)}{\bf November 2017 - February 2022}{}{}

    \item Built full stack architecture with MongoDB, 
    \item Developed a scalable Recipe parser and has successfully parsed 2M+ recipes
    \item Wireframed and designed mobile and web interface
    \item Built customer support channels to gather customer feedback allowing us prioritize feature development and bug fixes
    \item Developed recipe search engine with MongoDB Atlas Search enabling customers to search recipes by name, ingredient, and category
    \item Negotiated and completed the sale of RecipeBox assets to eMeals.com
    \item Built customer funnels to measure user conversion and engagement 
    
    \end{rSubsection}

    %------------------------------------------------

    \begin{rSubsection}{Mobile Solutions Architect at Wyndham Destinations}{\bf August 2018 - February 2022}{}{}

    \item Managed a team of 20+ engineers across mobile, web, embedded, hardware, and automated testing disciplines. Coordinated dependencies between teams to minimize workflow bottlenecks.
    \item Developed deployment schedule 
    \item Managed iOS applications
    \item Led cross discipline initiatives 
    \item Change advisory board
    \item Collaborated with product, account, and quality teams to ensure deliverables met our customers' expectations. Partnered with the product team to write product requirement documents.
    \item Developed a hiring plan and managed our recruiting and hiring processes to attract great talent to the company. Oversaw recruitment, interviewing, hiring, and onboarding.
    \item Managed our residential customer accounts and collaborated to design innovative residential access control products.

    \end{rSubsection}

    %------------------------------------------------

    \begin{rSubsection}{Engineering Manager / Head of Residential at UniKey Technologies}{\bf March 2017 - July 2018}{}{}

    \item Managed a team of 20+ engineers across mobile, web, embedded, hardware, and automated testing disciplines. Coordinated dependencies between teams to minimize workflow bottlenecks.
    \item Provided individual guidance and coaching through weekly 1:1s to help teammates achieve professional goals.
    \item Developed and implemented engineering processes to improve communication and development workflows within the company.
    \item Maintained project schedules and ensured deliverables were produced on time and on budget.
    \item Collaborated with product, account, and quality teams to ensure deliverables met our customers' expectations. Partnered with the product team to write product requirement documents.
    \item Developed a hiring plan and managed our recruiting and hiring processes to attract great talent to the company. Oversaw recruitment, interviewing, hiring, and onboarding.
    \item Managed our residential customer accounts and collaborated to design innovative residential access control products.

    \end{rSubsection}

    %------------------------------------------------

    \begin{rSubsection}{Mobile Engineering Lead / Senior Software Engineer, Mobile at UniKey Technologies}{\bf August 2015 - March 2017}{}{}

    \item Managed a team of six engineers developing iOS and Android applications for customers in the access control industry. 
    \item Facilitated weekly 1:1s with individual teammates and helped them achieve professional goals.
    \item Led efforts to whitelabel our flagship product, Kevo, to allow customers to get to market faster while reducing engineering time.
    \item Worked to implement continuous integration to allow our team to deliver mobile builds more frequently and consistently.
    \item Ensured work was planned and logged into JIRA to give other teams insight into the progress of their projects.

    \end{rSubsection}

    %------------------------------------------------

    \begin{rSubsection}{Lead Mobile Engineer at Echo Interaction Group}{\bf February 2014 - August 2015}{}{}

    \item Led a team of six engineers in a fast paced environment to produce mobile applications for our customers.
    \item Developed estimates and assisted on the bidding process for contract opportunities.
    \item Interfaced with our clients and their technical teams to gather requirements, generate specifications, and put a development plan in place.
    \item Maintained high code and product quality standards.


    \end{rSubsection}

    %------------------------------------------------

    \begin{rSubsection}{Lead Mobile Developer at AAA}{\bf October 2012 - February 2014}{}{}

    \item Oversaw the development and deployment of mobile applications installed on over 1M devices.
    \item Prototyped experimental products to help users plan and and enjoy their vacations.
    \item Collaborated with multiple business lines to bring visibility to their products within AAA's mobile properties.

    \end{rSubsection}


\end{rSection}

%----------------------------------------------------------------------------------------
%	COMMUNITY CONTRIBUTIONS
%----------------------------------------------------------------------------------------

\begin{rSection}{Education and Achivements}

    {\bf University of Central Florida} \hfill {\bf 2010} \\ 
    {\it Bachelor of Science}: Information Technology \\

\begin{rSubsection}{Captain at Code for Orlando}{\bf September 2014 - May 2018}{}{}

\item Built an effective leadership team to address the day to day challenges of running a Code for America brigade.
\item Coordinated and ran community "hack nights" to provide space for our members to tackle problems in our community.
\item Grew the brigade to over 1700 diverse members from a range of backgrounds and disciplines.
\item Developed and maintained relationships with city employees and collaborated on joint projects.
\item Planned and administered events for Code for America's National Day of Civic Hacking and CodeAcross.


\end{rSubsection}

\begin{rSubsection}{National Advisory Council at Code for America}{\bf September 2016 - February 2018}{}{}

\item Elected by my peers to sit on Code for America's National Advisory Council.
\item Participated in strategic planning meetings to strengthen the brigade network.
\item Issued the closing statement at Code for America's inaugural Brigade Congress event.


\end{rSubsection}

\begin{rSubsection}{Founder of Orlando iOS Developer Meetup}{\bf April 2011 - April 2017}{}{}

\item Coordinated events to bring together makers interested in furthering their iOS engineering skills.
\item Grew the network from scratch to over 1500 members in six years.
\item Networked with the iOS engineering community to recruit speakers on topics relevant to iOS development.


\end{rSubsection}

\end{rSection}


%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills}

    \textbf{Languages/Frameworks:} Swift, Objective C, Cocoa Touch, Node.js, Express, SQL  \\
    \textbf{AWS:} S3, Lambda, SNS, SQS, IAM, Pinpoint, Step Functions, DynamoDB  \\
    \textbf{DevOps:} Jenkins, Fastlane, XCTest, HockeyApp, Fabric, TestFlight \\
    \textbf{Databases/ORMs:} CoreData, MySQL, MongoDb  \\
    \textbf{Tools:} Xcode, VS Code, Bitbucket, Git, JIRA, MS Project, Photoshop  \\
    
    \end{rSection}


\end{document}
