%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Victor Rivera-Marquez}
\address{Github: github.com/LunarXer0}
\address{LinkedIn: bit.ly/2npiNXT}
\address{verm2405@gmail.com}



\begin{document}


%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills}

\textbf{Languages/Frameworks:} JavaScript, PHP, jQuery, CSS, BootStrap  \\
\textbf{Databases:} MySQL  \\
\textbf{Tools:} VS Code, Git, Asana  \\
\textbf{Spoken Languages:} Spanish, English  \\

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

%------------------------------------------------

\begin{rSubsection}{Full Stack Engineer, Contractor at The Right Profile}{\bf March 2018 - August 2018}{}{}

\item Designed and developed a user interface for our find players tool to asynchronously filter through players. Data is retrieved via AJAX to a PHP application that executes MySQL queries.
\item Integrated Google Charts into data reports and customized their visual style to improve data representation and provide a more modern feeling to the app.
\item Designed and developed a tool for users to be able to manage their subscriptions. Integrated the Stripe API to handle payment information using PHP and MySQL.
\item Took full ownership of the registration process from wireframe to development. Handled data validation, protected against SQL Injection, and stored new user accounts in MySQL.

\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Information Technology Intern at United Data Technologies}{\bf June 2015 - July 2015}{}{}

\item Migrated two financial departments at Santander Financial Bank onto a new floor by moving and setting up 40 personal workstations. 
\item Assisted in the installation of a new Cisco computer server to establish access between the new department floor and the bank’s network.
\item Performed the patching of all the new workstations onto the latest server software.

\end{rSubsection}


\end{rSection}

%----------------------------------------------------------------------------------------
%	Personal Projects
%----------------------------------------------------------------------------------------

\begin{rSection}{Personal Projects}

\begin{rSubsection}{MovieApp}{\bf }{}{}

\item Began developing this app using the LAMP stack. API calls to The Online Movie Database are executed in JavaScript. Login validation, data gathering and storage are handled by PHP, and MySQL.
\item As an exercise I am also developing this app using the MERN stack. This version makes use of more advanced coding practices like module patterns to increase scalability and maintainability as the codebase grows.
\item I am also using MERN to learn MongoDB and Express.
\item Data calls are handled API calls to The Online Movie Database via async \& await promises .


\end{rSubsection}

\begin{rSubsection}{Code Rookie YouTube Channel - https://bit.ly/2vtu2Ti}{\bf }{}{}

\item Created a Youtube channel called Code Rookie to document and share my knowledge as a self-taught web developer. 
\item I hope to use this channel as a platform to connect with my viewers, share my experiences and to inspire others to love programming.
\item I plan to talk about how I overcome the challenges I face in my journey as a junior engineer.


\end{rSubsection}
\end{rSection}


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education and Achievements}

{\bf University of Central Florida} \hfill {\bf 2013-2018} \\ 
{\it Bachelor of Science}: Information Technology \\
\end{rSection}

\end{document}
